% resume.tex: My current resume
%
% Name:		Calvin Owens
% E-Mail:	jcalvinowens@gmail.com
% Address: 	3410 Heather Hill Dr, Garland, TX 75044-2030
% Phone:	+12143647857
%
% This document is released into the public domain. This applies worldwide. In
% case this is not legally possible, the creator grants anyone the right to use
% this work for any purpose, without any conditions, unless such conditions are
% required by law.

\documentclass[11pt]{article}
\topmargin=-0.75in
\oddsidemargin=-0.75in
\evensidemargin=-0.75in
\textwidth=7.75in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=10.5in
\pagenumbering{gobble}

\usepackage{multicol}
\usepackage{enumitem}

\begin{document}

\centerline{{\Huge \sc Calvin Owens}}
\centerline{3410 Heather Hill Dr, Garland, TX 75044-2030}
\centerline{+12143647857 \textbullet \hspace{1pt} jcalvinowens@gmail.com}
\centerline{www.github.com/jcalvinowens}

\noindent
\hrulefill

\centerline{\underline{\bf Education}}
\bigskip
\noindent {\bf Southern Methodist University, Dallas, TX} \\
\indent \indent $\bullet$ B.M. Clarinet Performance \hfill May 2014\\
\indent \indent $\bullet$ B.A. Computer Science \hfill Graduating August 2014

\noindent
\hrulefill

\centerline{\underline{\bf Current/Past Employers}}
\bigskip
\noindent\centerline{\bf Backup Cave, LLC \hfill May 2014 - Present}
\underline{Position:} Backend Software Engineer, Co-founder. \\
\underline{Notable work:} Implementing a system for large-scale encrypted
backups, targeted at businesses and system administrators, in the vein of
Tarsnap. Notably, I simplify the end-user configuration significantly by using
password-derived EdDSA (Curve25519) keys for authentication. We hope to have a
functional prototype within a month. 
\vspace*{6pt}\\
\noindent\centerline{\bf Google Summer of Code \hfill May 2013 - October 2013}
\underline{Position:} Student participant, working for the Linux Foundation. \\
\underline{Notable work:} Implemented a system to avoid backing holes in sparse
files with real physical pages in the page cache. Currently refactoring the
patches, hoping to get them merged upstream in the near future.
\vspace*{6pt}\\
\noindent\centerline{\bf Highland Park High School \hfill January 2013 - Present}
\underline{Position:} Private clarinet instructor (Weekly half-hour lessons; 10 students).
\vspace*{6pt}\\
\noindent\centerline{\bf Docsystems, Inc. \hfill December 2012 - May 2014}
\underline{Position:} Backend programmer, database administrator, system administrator. \\
\underline{Notable work:} Created a charting system that dynamically calculates
a doctor's most probable next choice based on all past charts that doctor, any
doctor, or any specific subset of all doctors, filled out. Backend to frontend
communication used websockets; the backend was a daemon written in Python. I
used MongoDB (NoSQL) as the backend database.
\vspace*{6pt}\\
\noindent\centerline{\bf SMU School of Law \hfill December 2010 - August 2013}
\underline{Position:} IT Student Worker. \\
\underline{Notable work:} Set up a Linux multicast network hard drive cloning
machine, which can reimage an entire 30-workstation computer lab in under an
hour. The existing solution took 2-3 hours per computer.

\noindent
\hrulefill

\centerline{\underline{\bf Skills and Proficiencies}}

\begin{multicols}{2}

\centerline{\bf Programming Languages}
\bigskip
\noindent Highly proficient in:\\
\centerline{\hfill $\bullet$ C \hfill $\bullet$ Python \hfill $\bullet$ Shell Scripting \hfill}
\noindent Familiar with:\\
\centerline{\hfill $\bullet$ C++ \hfill $\bullet$ Java \hfill $\bullet$ JavaScript \hfill $\bullet$ Perl \hfill $\bullet$ PHP \hfill}
\noindent Assembly languages:\\
\centerline{\hfill $\bullet$ ARM \hfill $\bullet$ MIPS \hfill $\bullet$ x86 \hfill}

\bigskip

\centerline{\bf Skills}
\begin{itemize}[leftmargin=*]
\itemsep 0em
	\item Extremely well-versed in the setup and administration of Linux
	systems, particularly Gentoo and Debian.
	\item Intimately familiar with common networking protocols and configurations.
	\item Extensive knowledge of digital cryptography.
	\item In-depth knowledge of Linux Kernel functionality, programming, and debugging.
\end{itemize}

\columnbreak

\centerline{\bf Open Source Work}
\begin{itemize}[leftmargin=*]
\itemsep 0em
	\item Linux Kernel - 3 commits upstream:
	\begin{itemize}
	\itemsep 0em
		\item b1ea3e6e: Bugfix in the Nouveau GPU driver.
		\item 1539d4f8: Driver fix to support 192KHz recording on a certain USB sound card.
		\item dfa1ad29: Aesthetic addition to kdmesg output from IEEE 802.11 driver.
	\end{itemize}
	\item Personal projects:
	\begin{itemize}
	\itemsep 0em
		\item AsmHTTPd: Minimalist HTTP webserver, written entirely in x86-64 assembler.
		\item Chess-engine: Very simple chess AI, written in C.
		\item DataBlaster: Utility for sending files lossily over UDP at a constant bitrate.
	\end{itemize}
\end{itemize}

\end{multicols}

\end{document}
